Randomization and Traditional Examples using `okcupiddata` `profiles` data

### 2018-03-23 inst/doc/profiles_examples_both_methods.Rmd
Update pkgdown and vignettes

## Testing

@@

@@

### To Do (Also overlay appropriate chi-sq distn)

One categorical (>2 level) - GoF

```{r eval=FALSE, include=FALSE}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

@@

>>>>

@@

Randomization approach to $\chi^2$-statistic

@@

## One categorical (>2 level) - GoF

Randomization approach to $\chi^2$-statistic

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
#  generate(reps = 1000, type = "simulate") %>%
#  calculate(stat = "Chisq") %>% 
  visualize(method = "theoretical")
```

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both")
```

@@

<!-- ## Testing -->
